---
title: "Goal Project"
author: "Steven Mesquiti"
date: "`rSys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
```{r setup, include=FALSE, message=FALSE}
# set chunk options for the document
# include=FALSE means that this chunk will not show up in the report

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = FALSE, dpi = 150, fig.path = "figs/") 
# echo = TRUE means that the source code will be displayed
# message = FALSE suppresses messages
# warning = FALSE suppresses warnings
# cache = FALSE recompiles from scratch each time you knit 
# dpi = 150 sets the figure resolution
# fig.path specifies a directory where figures will be output

options(scipen = 999) #turn off scientific notation
set.seed(65) #set seed for random number generation
```
# Prep data {.tabset}
## Load necessary packages
```{r include=FALSE}
setwd("~/Desktop/goals project") 

if (!require("tidyverse")) install.packages("tidyverse")
if (!require("brms")) install.packages("brms")
if (!require("knitr")) install.packages("knitr")
if (!require("readr")) install.packages("readr")
if (!require("kableExtra")) install.packages("kableExtra")
if (!require("reactable")) install.packages("reactable")
if (!require("tidybayes")) install.packages("tidybayes")
if (!require("rstanarm")) install.packages("rstanarm")
if (!require("httr")) install.packages("httr")
if (!require("insight")) install.packages("insight")
if (!require("sjPlot")) install.packages("sjPlot")
if (!require("bayesplot")) install.packages("bayesplot")
if (!require("ggpubr")) install.packages("ggpubr")



library(dplyr)
library(ggplot2)
library(brms)
library(Brobdingnag)
library(tidyverse)
library(knitr)
library(readr)
library(kableExtra)
library(reactable)
library(tidybayes)
library(rstanarm)
library(httr)
library(sjPlot)
library(bayesplot)
library(ggpubr)

devtools::install_github("hadley/emo")

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

```

## Define aesthetics
```{r}
palette_map = c("#3B9AB2", "#EBCC2A", "#F21A00")
palette_condition = c("#ee9b00", "#bb3e03", "#005f73")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## Load data 
```{r}
data <- read_csv("disaggregated_data.csv") #read in data 
data$timepoint_num <- as.factor(data$timepoint_num) #set as a factor so our graphs can work 

```

## Tidy data
Data transformations

* None

Exclusions

* No participants were excluded

## Sample size
```{r}
sample <- data %>%
  select(timepoint, SID) %>%
  unique() %>%
  group_by(timepoint) %>%
  dplyr::summarize(n = n()) %>%
  reactable::reactable(striped = TRUE)
sample
```

# Data quality checks {.tabset}
## Missing data
```{r}
data %>%
  filter(is.na(progress)) %>%
  group_by(SID,timepoint) %>%
  dplyr::summarize(n = n()) %>%
  arrange(-n)
```

## Outliers {.tabset}
There do not appear to be obvious outliers

```{r}
progress <- data %>%
  ggplot(aes(timepoint, progress, fill = timepoint)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
  geom_point(aes(color = timepoint), position = position_jitter(width = .05), size = .1, alpha = .1) + 
  geom_boxplot(width = .1, outlier.shape = NA, fill = NA) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  scale_color_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  labs(x = "") +
  coord_flip() +
  plot_aes +
  theme(legend.position = "none")

autonomous_motivation_within <- data %>%
  ggplot(aes(timepoint, autonomous_motivation_within, fill = timepoint)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
  geom_point(aes(color = timepoint), position = position_jitter(width = .05), size = .1, alpha = .1) + 
  geom_boxplot(width = .1, outlier.shape = NA, fill = NA) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  scale_color_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  labs(x = "") +
  coord_flip() +
  plot_aes +
  theme(legend.position = "none")

controlled_motivation_within  <- data %>%
  ggplot(aes(timepoint, controlled_motivation_within, fill = timepoint)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
  geom_point(aes(color = timepoint), position = position_jitter(width = .05), size = .1, alpha = .1) + 
  geom_boxplot(width = .1, outlier.shape = NA, fill = NA) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  scale_color_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  labs(x = "") +
  coord_flip() +
  plot_aes +
  theme(legend.position = "none")

autonomous_motivation_between <- data %>%
  ggplot(aes(timepoint, autonomous_motivation_between, fill = timepoint)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
  geom_point(aes(color = timepoint), position = position_jitter(width = .05), size = .1, alpha = .1) + 
  geom_boxplot(width = .1, outlier.shape = NA, fill = NA) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  scale_color_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  labs(x = "") +
  coord_flip() +
  plot_aes +
  theme(legend.position = "none")

controlled_motivation_between <- data %>%
  ggplot(aes(timepoint, controlled_motivation_between, fill = timepoint)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
  geom_point(aes(color = timepoint), position = position_jitter(width = .05), size = .1, alpha = .1) + 
  geom_boxplot(width = .1, outlier.shape = NA, fill = NA) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  scale_color_manual(values = wesanderson::wes_palette("Zissou1", n = 4, type = "continuous")) +
  labs(x = "") +
  coord_flip() +
  plot_aes +
  theme(legend.position = "none")

descriptive_graphs <- ggpubr::ggarrange(progress,autonomous_motivation_within,controlled_motivation_within,
                                        autonomous_motivation_between,controlled_motivation_between ,ncol=2, nrow=3, common.legend = T, legend = "bottom")
descriptive_graphs
```
# Descriptive statistics  {.tabset}
## Goal Progress (Rating scale: 0-100%)
> What percentage of this project is completed right now?
## Motivation Rating (1 = not at all for this reason, 7 = completely for this reason)
> Please rate the extent to which you are working on this personal project because:

> It provides you fun and enjoyment

> You really believe it's an important goal to have

> You would feel ashamed, guilty, or anxious if you didn't

> Somebody else wants you to or because the situation demands it

>Items 1 and 2 will be averaged to create an index of autonomous motivation; items 3 and 4 will be averaged to create an index of controlled motivation.

```{r eval=FALSE, include=FALSE}
#means (need to work on later)
means = data %>%
  group_by(timepoint_num) %>%
  filter(!is.na(progress)) %>%
  summarize(N = n(),
            `M (SD)` = sprintf("%s (%s)", round(mean(progress, na.rm = TRUE), 2), round(sd(progress, na.rm = TRUE), 2))) %>%
  mutate(`scale range` = "0-100") %>%
  select(`scale range`, everything()) %>%
  rename("timepoint" = timepoint_num)
means
```


# Preregistered analyses 
The following hypotheses are preregistered. The preregistration is available on [OSF](https://osf.io/3pcnj)

## Primary Analyses 
> We estimated a single model to test H1 and H2 using noninformatie priors (mu = 0, sigma = 5). 

## Hypothesis 1 
> H1 Between-person: People who tend to have more autonomous goals compared to others will show greater goal progress

## Results {.tabset}
`r emo::ji("x")` These data are ***not*** consistent with the hypothesis that people who tend to have more autonomous goals compared to others will show greater goal progress

```{r include=FALSE}
#these options help speed up estimation 
options(mc.cores = parallel::detectCores())

#####Hypothesis 1 
#set our weakly informative prior 
h1_prior <- c(set_prior("normal(0, 5)", class = "b"),
              set_prior("normal(0, 5)", class = "Intercept")) 

#run our model, which may take a few moments
mod_h1 <- brm(progress ~ timepoint_num + autonomous_motivation_between + autonomous_motivation_between * timepoint_num + autonomous_motivation_within +
                autonomous_motivation_within * timepoint_num + (1 + autonomous_motivation_within * timepoint_num | SID), 
              prior = h1_prior, data = data, sample_prior = TRUE)
```
### Look at our model
```{r}
mod_h1 #check out our model
```

### Plot Conditional Effects of Within Person Differences * time (H1)
```{r}
####Plotting conditional effects#######################3####
#between * time 
between_cond <- conditional_effects(mod_h1, effect = 'autonomous_motivation_between:timepoint_num') #conditional effects 
est_bw <- as.data.frame(between_cond[[1]])
cond_between<- ggplot()  +
  xlab('Change in Within-Person Autonomous Motivation') +
  ylab('Goal Progress') + 
  geom_pointrange(aes(autonomous_motivation_between, estimate__, ymin = lower__, ymax = upper__, color = timepoint_num), 
                  est_bw, position = position_dodge(width = .5)) +theme_minimal() + 
  scale_colour_manual(values = c('red', 'blue'),
                      labels = c("Check-in", "Follow-up")) +theme_bw()
cond_between
```
### Plot our Posteriors Between-person differences in autonomous motivation (H1)
```{r}
h_posterior <- as.matrix(mod_h1)

h1_plots <- mcmc_areas(h_posterior,
           pars = c("b_autonomous_motivation_between", 
                    "b_timepoint_num1:autonomous_motivation_between" ),
           prob = 0.95, point_est = "median")


h1_plots <- h1_plots + labs(x = "Value", y = 'Parameter')+  theme(axis.text=element_text(size=16),
                                                   axis.title=element_text(size=20,face="bold")) +
  ggplot2::scale_y_discrete(labels = c("Autonomous Motivation Between", "Autonomous Motivation Between * Time"))

annotate_figure(h1_plots,
                top = text_grob("Between Person Posterior distributions",  color = "black", face = "bold", size = 20),
                bottom = text_grob("Note. Estimates presented are medians within the 95% Credible Intervals."
                                   , color = "Black",
                                   hjust = 1.1, x = 1, face = "italic", size = 16))


h_posteriors <- get_parameters(mod_h1)
bayestestR::hdi(h_posteriors$b_autonomous_motivation_within)
```
### Look at Influence of Priors
```{r}
hplot1 <- plot(hypothesis(mod_h1, "autonomous_motivation_between > 0")) #shows how influential our priors were on our posteriors
hplot2 <- plot(hypothesis(mod_h1,"timepoint_num1:autonomous_motivation_between > 0")) #shows how influential our priors were on our posteriors
```
## Hypothesis 2 
>  H2 Within-person: Goals that are more autonomous compared to a person’s average will be associated with greater progress

## Results {.tabset}
`r emo::ji("check")` These data are consistent with the hypothesis that thinking about the self-relevance of a message increases its perceived self-relevance
### Plot Conditional Effects of Within Person Differences * time 
```{r}
within_cond <- conditional_effects(mod_h1, effect = 'autonomous_motivation_within:timepoint_num') #conditional effects 

est_within <- as.data.frame(within_cond[[1]])
cond_within<- ggplot()  +
  xlab('Change in Within-Person Autonomous Motivation') +
  ylab('Goal Progress') + 
  geom_pointrange(aes(autonomous_motivation_within, estimate__, ymin = lower__, ymax = upper__, color = timepoint_num), 
                  est_within, position = position_dodge(width = .5)) +theme_minimal() + 
  scale_colour_manual(values = c('red', 'blue'),
                      labels = c("Check-in", "Follow-up")) +theme_bw()
cond_within
```
### Plot our Posteriors for H2
```{r}
#main effect of autonomous(within)
#Plot posteror 
h2_plots <- mcmc_areas(h_posterior,
                       pars = c("b_autonomous_motivation_within", 
                                "b_timepoint_num1:autonomous_motivation_within",
                                "sd_SID__autonomous_motivation_within",
                                "sd_SID__autonomous_motivation_within:timepoint_num1" ),
                       prob = 0.95, point_est = "median") 

h2_plots <- h2_plots + labs(x = "Value", y = 'Parameter')+  theme(axis.text=element_text(size=16),
                                                                  axis.title=element_text(size=20,face="bold")) +
  ggplot2::scale_y_discrete(labels = c("Autonomous Motivation Within", "Autonomous Motivation Within * Time", 
                                       "Autonomous Motivation Within (Random Effects)", ("Autonomous Motivation Within * Time (Random Effects)")))

annotate_figure(h2_plots,
                top = text_grob("Within-Person Posterior Distributions ",  color = "black", face = "bold", size = 20),
                bottom = text_grob("Note. Estimates presented are medians within the 95% Credible Intervals."
                                   , color = "Black",
                                   hjust = 2.2, x = 1, face = "italic", size = 16))
```
### Look at Infuence of Priors
```{r}
hplot3 <- plot(hypothesis(mod_h1,"autonomous_motivation_within > 0")) #shows how influential our priors were on our posteriors
hplot4 <- plot(hypothesis(mod_h1,"timepoint_num1:autonomous_motivation_within > 0")) #shows how influential our priors were on our posteriors
```


# Exploratory analyses 
> We will estimate a single model to test E1 and E2. The coefficient that will be interpreted is highlighted for each research question below.

## Exploratory Hypothesis 1 
> E1 Between-person : Are people who tend to have more controlled goals compared to others more or less successful at pursuing their goals?

```{r}
####Exploratory###############################################
e1_prior <- c(set_prior("normal(0, 5)", class = "b"),
              set_prior("normal(0, 5)", class = "Intercept")) #set our weakly informative prior 


#run model
mod_e1 <- brm(progress ~ timepoint_num + controlled_motivation_between + controlled_motivation_between * timepoint_num + controlled_motivation_within +
                controlled_motivation_within * timepoint_num + (1 + controlled_motivation_within * timepoint_num | SID),
              prior  =  e1_prior, data = data, sample_prior = TRUE)

```
## Results E1 {.tabset}
> `r emo::ji("x")` These data are ***not*** consistent with the hypothesis that people who tend to have more controlled goals compared to others will show greater goal progress

### Look at our model.
```{r}
summary(mod_e1)
```

### Plot condiitonal effects of Between Person Controlled Motivation * Time
```{r}
e_between_cond <- conditional_effects((mod_e1), effect = ('controlled_motivation_between:timepoint_num')) #conditional effects 

est_bw <- as.data.frame(e_between_cond[[1]])
e_cond_between<- ggplot()  +
  xlab('Change in Between-Person Controlled Motivation') +
  ylab('Goal Progress') + 
  geom_pointrange(aes(controlled_motivation_between, estimate__, ymin = lower__, ymax = upper__, color = timepoint_num), 
                  est_bw, position = position_dodge(width = .5)) +theme_minimal() + 
  scale_colour_manual(values = c('red', 'blue'),
                      labels = c("Check-in", "Follow-up")) +theme_bw()
e_cond_between
```

### Plot Posterior for Between Person Differences in Controlled Motivation (E1)
```{r}
#E1 Hypothesis
#Plot posteriors 
#build matrix to build graphs
e_posterior <- as.matrix(mod_e1)

e1_plots <- mcmc_areas(e_posterior,
                       pars = c("b_controlled_motivation_between", 
                                "b_timepoint_num1:controlled_motivation_between" ),
                       prob = 0.95, point_est = "median")


e1_plots <- e1_plots + labs(x = "Value", y = 'Parameter')+  theme(axis.text=element_text(size=16),
                                                                  axis.title=element_text(size=20,face="bold")) +
  ggplot2::scale_y_discrete(labels = c("Controlled Motivation Between", "Controlled Motivation Between * Time"))

annotate_figure(e1_plots,
                top = text_grob("Between Person Posterior distributions",  color = "black", face = "bold", size = 20),
                bottom = text_grob("Note. Estimates presented are medians within the 95% Credible Intervals."
                                   , color = "Black",
                                   hjust = 1.1, x = 1, face = "italic", size = 16))
```

## Exploratory Hypothesis 2 
> E2 Within-person: Do goals that are more controlled compared to a person’s average lead to higher or lower success?

## Results E2 {.tabset}
> `r emo::ji("x")` These data are consistent with the hypothesis that goals that are more controlled...
### Plot condiitonal effects of Within-Person Controlled Motivation * Time (E2)
```{r}
e_within_cond <- conditional_effects((mod_e1), effect = ('controlled_motivation_within:timepoint_num')) #conditional effects 

est_within <- as.data.frame(e_within_cond[[1]])
e_cond_within<- ggplot()  +
  xlab('Change in Within-Person Controlled Motivation') +
  ylab('Goal Progress') + 
  geom_pointrange(aes(controlled_motivation_within, estimate__, ymin = lower__, ymax = upper__, color = timepoint_num), 
                  est_within, position = position_dodge(width = .5)) +theme_minimal() + 
  scale_colour_manual(values = c('red', 'blue'),
                      labels = c("Check-in", "Follow-up")) +theme_bw()
e_cond_within
```
### Plot Posteriors for Within-Person Differences in Controlled Motivation (E2)
```{r}
e2_plots <- mcmc_areas(e_posterior,
                       pars = c("b_controlled_motivation_within", 
                                "b_timepoint_num1:controlled_motivation_within",
                                "sd_SID__controlled_motivation_within",
                                "sd_SID__controlled_motivation_within:timepoint_num1" ),
                       prob = 0.95, point_est = "median") 


e2_plots <- e2_plots + labs(x = "Value", y = 'Parameter')+  theme(axis.text=element_text(size=16),
                                                                  axis.title=element_text(size=20,face="bold")) +
  ggplot2::scale_y_discrete(labels = c("Controlled Motivation Within", "Controlled Motivation Within * Time", 
                                       "Controlled Motivation Within (Random Effects)", ("Controlled Motivation Within * Time (Random Effects)")))

annotate_figure(e2_plots,
                top = text_grob("Within-Person Posterior Distributions ",  color = "black", face = "bold", size = 20),
                bottom = text_grob("Note. Estimates presented are medians within the 95% Credible Intervals."
                                   , color = "Black",
                                   hjust = 2.2, x = 1, face = "italic", size = 16))
```