---
title: "Goal visualization"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

options(scipen=999)
```

# load packages
```{r}
library(pacman)
pacman::p_load(tidyverse, install = TRUE)
```

# define aesthetics
```{r}
palette = wesanderson::wes_palette("Zissou1", n = 2, type = "continuous")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 8),
        text = element_text(size = 10, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

# load data
Create high / low motivation variables based on being > the grand mean (between-person) or a person's mean (within-person), or =< to it.

```{r}
data = read.csv("../data/disaggregated_data.csv") %>%
  mutate(`autonomous motivation (between)` = ifelse(autonomous_motivation_between > 0, "high", "low"),
         `autonomous motivation (within)` = ifelse(autonomous_motivation_within > 0, "high", "low"),
         timepoint = recode(timepoint, "Check In" = "Start", "Follow Up" = "Finish"),
         timepoint = factor(timepoint, levels = c("Start", "Finish"))) %>%
  select(SID, wave, timepoint, goal_number, progress, contains("("))
```

# visualize data {.tabset}
## within-person
```{r, fig.width=6, fig.height=6}
data %>%
  filter(!is.na(`autonomous motivation (within)`)) %>%
  ggplot(aes(timepoint, progress, color = `autonomous motivation (within)`)) +
  geom_line(aes(group = interaction(SID, goal_number, wave)), alpha = .1) +
  scale_color_manual(values = palette) +
  plot_aes +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  scale_x_discrete(expand = c(.1, .1))

```

## between-person
```{r, fig.width=6, fig.height=6}
data %>%
  filter(!is.na(`autonomous motivation (between)`)) %>%
  group_by(SID, timepoint, `autonomous motivation (between)`) %>%
  summarize(`mean progress` = mean(progress, na.rm = TRUE)) %>%
  ggplot(aes(timepoint, `mean progress`, color = `autonomous motivation (between)`)) +
  geom_line(aes(group = interaction(SID)), alpha = .5) +
  scale_color_manual(values = palette) +
  plot_aes +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  scale_x_discrete(expand = c(.1, .1))

```
